Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/related.tex
Update on Overleaf.

\paragraph{Dense Libraries:} There are many well known libraries that specialize in dense computations, exemplified by BLAS, though several BLAS routines are specialized to symmetric, hermitian, and triangular matrices~\cite{Anderson1999}.
%
This pattern is carried over into well known dense array libraries that use BLAS, exemplified by Numpy

%

@@

>>>>

\paragraph{Dense Libraries:} There are many well known libraries that specialize in dense computations, exemplified by BLAS, though several BLAS routines are specialized to symmetric, hermitian, and triangular matrices~\cite{Anderson1999}.
%
This pattern is carried over into well known dense array libraries that use BLAS, exemplified by Numpy.

@@

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, and COO.
%
Examples include Scipy, PETSc, Armadillo, and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, eigenweb}.
